---
title: "Combating World Hunger through Data Analysis: Project Proposal"
author: "Asad Jaffery, Beliz Ozhan, Curt Tanaka"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r echo=FALSE, eval=TRUE, message=FALSE}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)

source("../source/summary_information.R")
source("../source/undernourishment_chart_code.R")
source("../source/countrywide_average_code.R")

```


# Summary of Datasets:
Since we are studying world hunger, we decided to use our in order to determine which countries are in the worst conditions and which are in the best conditions. `r highest_underweight1` is the country that has the highest percentage of population that is considered to be 'underweight', while `r lowest_underweightr` is the country with the lowest percentage of underweight population. Next, we examined our undernourishment data set in order to find that `r highest_undernourishment1` is the country with the highest percentage of population undernourished, whereas `r lowest_undernourishment1`, are all tied for the lowest percentage of population of undernourished. Lastly, it is important to understand the global hunger index (GHI), which tracks hunger by region. `r highest_GHI1` has the highest GHI score, and `r lowest_GHI1` are all tied for the lowest.
\n


# Underweight Population by Country
```{r echo=FALSE, eval=TRUE, message=FALSE}
plot_underweight_pop_country()
```



The chart depicting underweight population by country represents the total population of each country that is underweight. The reason we selected this dataset is because malnutrition is continuously a growing problem and makes people's health more vulnerable. This original data set includes many other data points about each country including the percent of the population which is  "wasting", “overweight", “stunting" , or “underweight". We selected the “underweight” category as it best answered our research question of how to combat world hunger and where efforts need to be made the most, based on the percentage of underweight people. 


\n

# Undernourishment by Countries
```{r echo=FALSE, eval=TRUE, message=FALSE}
plot_undernourishment_by_countries(c("Afghanistan", "Belize", "Ethiopia", "Thailand"))
```


This chart depicts the prevalence of undernourishment by country and by year. This percentage is based on the total population of each country by year, respectively. Through trends in the dataset we can see that for many countries the total prevalence of undernourishment is decreasing, but still continues to be a pressing problem for developing or third world countries. It is important to track the prevalence of undernourishment both by year and country to accurately understand the problem of hunger across the world. 


